---
title:  'Project: Study on building parameters'
subtitle: 'ISTA 421/INFO 521'
author:
- name: Student -  [Sudan Pandey]
  affiliation: [CAEM]
- name: Instructor -  Cristian Roman-Palacios
  affiliation: School of Information, University of Arizona, Tucson, AZ
tags: [R, RStudio, Project]
format:
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
---

This code is to check the correlation of the building parameters, particularly to find the better predictor of the alpha parameter. And index based on GA/EI is selected later to model the linear model to predict the alpha value. Alpha value is an important non dimensional paramter of a building which can be used to define the modal properties of the high rise building.


```{r}
# Load building data
library(ISLR)
building <- read.csv("Building.csv")
summary(building)
```


```{r}
# Correlation study
library(ISLR2)
library(corrplot)
pairs(building[, 2:13]) 
  cor(building[, 2:13])
cor.mat <- cor(building[, 2:13])
corrplot::corrplot(cor.mat)

#End
```


```{r}
# Define libraries and load data
library(ISLR2)
require(ggplot2)
require(caret)
require(tidyverse)
rawdata <- read.csv("Rawdata.csv")
summary(rawdata)
```

```{r}
# Spliting Data
head(rawdata)
dim(rawdata)
set.seed(1)

plot(rawdata,col = "blue")

inTrain <- createDataPartition(rawdata$a, p = 0.80, list = FALSE)

training <- rawdata[inTrain, ]
testing <- rawdata[-inTrain, ]

y_train <- training$a
y_test <- testing$a

x_train <- training$x
x_test <- testing$x

# END Splitting
```

  
```{r}
# Linear model
lin_model <- lm(a ~ ., data = training)
pred <- predict(lin_model, testing)
(lin_info <- postResample(pred, testing$a))
summary(lin_model)
summary(pred)

# END
```
